A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Updated the intro text of V

The corpus for this study includes R programs extracted from popular R packages
as well as complete user-written data-analysis scripts. In this section we
describe the methodology used to collect them.

\subsection{CRAN Packages}\label{sec:corpus}

@@

To represent user-written code in the corpus, we truned to
Kaggle\footnote{\url{https://www.kaggle.com}}, an online platform for
data-science and machine-learning practitioner. Among others, the website allow
people to share data-science competitions, a data-analysis problem together with
data, for which users try to find the best solution. The solutions, called
\emph{kernels}, are then shared back to the platform in the form of either plain
scripts or as Rmarkdown / Jupyter notebooks written in either Julia, Python, R
or SQLite.

@@

\begin{table}[ht]
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}r|ccc@{}} \hline
Source & Core & Dependent & Own \\\hline
      %      CRAN & \CranCoreTotalEvalCallsRnd (\CranCoreMinEvalCallsRnd/\CranCoreAvgEvalCallsRnd/\CranCoreMaxEvalCallsRnd) & \CranDependentTotalEvalCallsRnd (\CranDependentMinEvalCallsRnd/\CranDependentAvgEvalCallsRnd/\CranDependentMaxEvalCallsRnd) & \CranOwnTotalEvalCallsRnd (\CranOwnMinEvalCallsRnd/\CranOwnAvgEvalCallsRnd/\CranOwnMaxEvalCallsRnd) \\
CRAN & \CranCoreTotalEvalCallsRnd (1 / 581 / 416K)  & \CranDependentTotalEvalCallsRnd (1 / 532 / 183K) & \CranOwnTotalEvalCallsRnd (1 / 292 / 144K)\\
Kaggle & \KaggleCoreTotalEvalCallsRnd (1 / 412 / 2.8K) & \KaggleDependentTotalEvalCallsRnd (3 / 96 / 1.1K) & 0 (0 / 0 / 0) \\
%      Kaggle & \KaggleCoreTotalEvalCallsRnd (\KaggleCoreMinEvalCallsRnd/\KaggleCoreAvgEvalCallsRnd/\KaggleCoreMaxEvalCallsRnd) & \KaggleDependentTotalEvalCallsRnd (\KaggleDependentMinEvalCallsRnd/\KaggleDependentAvgEvalCallsRnd/\KaggleDependentMaxEvalCallsRnd) & 0(0/0/0) \\
      \hline
    \end{tabular}
  }
  \label{A}
  \caption{Eval calls in CRAN and Kaggle}
\end{table}

>>>>

In this study, we report on eval usage in a corpus of \CorpusCorePackages R core
and \CorpusPackages popular CRAN packages. To quantify the eval use, we run
\CorpusAllProgramsRnd of R programs that are extracted form those packages as
well as from the user-written data-analyses shared on the Kaggle platform. In
this section we describe this corpus and methodology used to assemble it.

\subsection{CRAN Packages}

@@

To represent user-written code in the corpus, we turned to
Kaggle\footnote{\url{https://www.kaggle.com}}, an online platform for
data-science and machine-learning practitioner. Among others, the website allow
people to share data-science competitions, a data-analysis problem together with
data, for which users try to find the best solution. The solutions, called
\emph{kernels}, are then shared back to the platform in the form of either plain
scripts or as Rmarkdown / Jupyter notebooks written in either Julia, Python, R
or SQLite.

@@

\begin{table}[ht]
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}r|ccc@{}} \hline
Source & Core & Dependent & Own \\\hline
      %      CRAN & \CranCoreTotalEvalCallsRnd (\CranCoreMinEvalCallsRnd/\CranCoreAvgEvalCallsRnd/\CranCoreMaxEvalCallsRnd) & \CranDependentTotalEvalCallsRnd (\CranDependentMinEvalCallsRnd/\CranDependentAvgEvalCallsRnd/\CranDependentMaxEvalCallsRnd) & \CranOwnTotalEvalCallsRnd (\CranOwnMinEvalCallsRnd/\CranOwnAvgEvalCallsRnd/\CranOwnMaxEvalCallsRnd) \\
CRAN & \CranCoreTotalEvalCallsRnd (1 / 581 / 416K)  & \CranDependentTotalEvalCallsRnd (1 / 532 / 183K) & \CranOwnTotalEvalCallsRnd (1 / 292 / 144K)\\
Kaggle & \KaggleCoreTotalEvalCallsRnd (1 / 412 / 2.8K) & \KaggleDependentTotalEvalCallsRnd (3 / 96 / 1.1K) & 0 (0 / 0 / 0) \\
%      Kaggle & \KaggleCoreTotalEvalCallsRnd (\KaggleCoreMinEvalCallsRnd/\KaggleCoreAvgEvalCallsRnd/\KaggleCoreMaxEvalCallsRnd) & \KaggleDependentTotalEvalCallsRnd (\KaggleDependentMinEvalCallsRnd/\KaggleDependentAvgEvalCallsRnd/\KaggleDependentMaxEvalCallsRnd) & 0(0/0/0) \\
      \hline
    \end{tabular}
  }
  \caption{Eval calls in CRAN and Kaggle}
  \label{A}
\end{table}
